### 2023-06-01 paper/localpsf.tex
move stokes pcg and geigs plots to separate files

\begin{figure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{impulse_batch1.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{impulse_batch2.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{impulse_batch3.png}
	\end{subfigure}
	\caption{Batches, $\eta_b$, of normalized impulses, $\impulseresponse_{x}$, for the Stokes inverse problem data misfit Gauss-Newton Hessian (Section~\ref{sec:numerical_results}). 
%	Brightness scale differs between the subfigures. 
	Black stars are point source locations. Dashed gray ellipses are estimated impulse response support ellipsoids. The large circle is $\partial \Omega$. 
	}
	\label{fig:batches_intro}
\end{figure}

@@

	\begin{subfigure}{0.49\textwidth}

@@

		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
		ymode=log,
		ymin=1e-13,
		ymax=2,
		xmax=750,
		axis x line*=bottom,
		axis y line*=left,
		xtick={0, 200, 400, 600},
		title={CG convergence},
		xlabel={$k$, CG iteration},
		ylabel={$\|\bm{x}_k-\bm{x}\|/\|\bm{x}\|$},
		legend style={at={(1.1,1)},anchor=north east},
		%legend pos=north east,
		legend style={font=\small}
		]
		\addlegendentry{Reg}		
		\addplot[dotted, line width=0.5mm] table {cg_relres_reg_0.05noise.dat};
		\addlegendentry{None}
		\addplot[dash dot, line width=0.5mm] table {cg_relres_none_0.05noise.dat};
		\addlegendentry{PSF (1)}
		\addplot[blue, line width=0.5mm] table {cg_relres_psf1_0.05noise.dat};
		\addlegendentry{PSF (5)}
		\addplot[red, line width=0.5mm] table {cg_relres_psf5_0.05noise.dat};
		\addlegendentry{PSF (25)}
		\addplot[purple, line width=0.5mm] table {cg_relres_psf25_0.05noise.dat};
		\end{axis}
		\end{tikzpicture}

@@

	\begin{subfigure}{0.49\textwidth}

@@

		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
		ymode=log,
		xmin=-50,
		xmax=1450,
		ymax=1.e7,
		title={Generalized eigenvalues},
		xlabel={$k$, generalized eigenvalue \#},
		ylabel={$\lambda_{k}$},
		xtick={0, 300, 600, 900, 1200},
		%legend pos=north east,
		legend style={font=\small},
		ylabel near ticks, ylabel shift={-6pt},
		axis x line*=bottom,
		axis y line*=right,
		%legend style={at={(0.95,1)},anchor=north east},
		]
		%\addlegendentry{REG}
		\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues_0.05noise.dat};
		\addplot[dash dot, line width=0.5mm] table[x=k, y=none] {generalizedEigenvalues_0.05noise.dat};
		%\addlegendentry{PSF (1)}
		\addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues_0.05noise.dat};
		%\addlegendentry{PSF (5)}
		\addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues_0.05noise.dat};
		%\addlegendentry{PSF (25)}
		\addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues_0.05noise.dat};
		\end{axis}
		\end{tikzpicture}

>>>>

\begin{figure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.34]{impulse_batch1.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.34]{impulse_batch2.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.34]{impulse_batch3.png}
	\end{subfigure}
	\caption{Batches, $\eta_b$, of normalized impulses, $\impulseresponse_{x}$, for the Stokes inverse problem data misfit Gauss-Newton Hessian (Section~\ref{sec:numerical_results}). 
%	Brightness scale differs between the subfigures. 
	Black stars are point source locations. Dashed gray ellipses are estimated impulse response support ellipsoids. The large circle is $\partial \Omega$. 
	}
	\label{fig:batches_intro}
\end{figure}

@@

	\begin{subfigure}{0.52\textwidth}

@@

		\includegraphics[scale=1.0]{stokes_pcg_convergence.pdf}
%		\begin{tikzpicture}[baseline, trim axis right]
%		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
%		ymode=log,
%		ymin=1e-13,
%		ymax=2,
%		xmax=750,
%		axis x line*=bottom,
%		axis y line*=left,
%		xtick={0, 200, 400, 600},
%		title={CG convergence},
%		xlabel={$k$, CG iteration},
%		ylabel={$\|\bm{x}_k-\bm{x}\|/\|\bm{x}\|$},
%		legend style={at={(1.1,1)},anchor=north east},
%		%legend pos=north east,
%		legend style={font=\small}
%		]
%		\addlegendentry{Reg}		
%		\addplot[dotted, line width=0.5mm] table {cg_relres_reg_0.05noise.dat};
%		\addlegendentry{None}
%		\addplot[dash dot, line width=0.5mm] table {cg_relres_none_0.05noise.dat};
%		\addlegendentry{PSF (1)}
%		\addplot[blue, line width=0.5mm] table {cg_relres_psf1_0.05noise.dat};
%		\addlegendentry{PSF (5)}
%		\addplot[red, line width=0.5mm] table {cg_relres_psf5_0.05noise.dat};
%		\addlegendentry{PSF (25)}
%		\addplot[purple, line width=0.5mm] table {cg_relres_psf25_0.05noise.dat};
%		\end{axis}
%		\end{tikzpicture}

@@

	\begin{subfigure}{0.47\textwidth}

@@

		\includegraphics[scale=1.0]{stokes_geigs_figure.pdf}
%		\begin{tikzpicture}[baseline, trim axis right]
%		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
%		ymode=log,
%		xmin=-50,
%		xmax=1450,
%		ymax=1.e7,
%		title={Generalized eigenvalues},
%		xlabel={$k$, generalized eigenvalue \#},
%		ylabel={$\lambda_{k}$},
%		xtick={0, 300, 600, 900, 1200},
%		%legend pos=north east,
%		legend style={font=\small},
%		ylabel near ticks, ylabel shift={-6pt},
%		axis x line*=bottom,
%		axis y line*=right,
%		%legend style={at={(0.95,1)},anchor=north east},
%		]
%		%\addlegendentry{REG}
%		\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues_0.05noise.dat};
%		\addplot[dash dot, line width=0.5mm] table[x=k, y=none] {generalizedEigenvalues_0.05noise.dat};
%		%\addlegendentry{PSF (1)}
%		\addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues_0.05noise.dat};
%		%\addlegendentry{PSF (5)}
%		\addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues_0.05noise.dat};
%		%\addlegendentry{PSF (25)}
%		\addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues_0.05noise.dat};
%		\end{axis}
%		\end{tikzpicture}

### 2023-06-01 paper/stokes_pcg_convergence.tex
move stokes pcg and geigs plots to separate files

\begin{document}
	\begin{tikzpicture}[baseline]%, trim axis right]
		\begin{axis}[width=0.49\linewidth, height=0.5\linewidth,
		ymode=log,
		ymin=1e-11,
		ymax=2,
		xmax=1000,
		axis x line*=bottom,
		axis y line*=left,
		xtick={0, 200, 400, 600,800,1000},
		xlabel={CG iteration},
		ylabel={$\|\bm{x}_k - \bm{x}\|/\|\bm{x}\|$},
		title={CG convergence},
		legend style={at={(1.2,1)},anchor=north east,draw=none},
		%legend pos=north east,
		legend style={font=\small}
		]
			\addlegendentry{Reg}
			\addplot[dotted, line width=0.5mm] table {advDiff_cg_rand_errs_reg.dat};
			\addlegendentry{None}
			\addplot[dash dot, line width=0.5mm] table {advDiff_cg_rand_errs_none.dat};
			\addlegendentry{PSF (1)}
			\addplot[blue, line width=0.5mm] table {advDiff_cg_rand_errs_psf1.dat};
			\addlegendentry{PSF (5)}
			\addplot[red, line width=0.5mm] table {advDiff_cg_rand_errs_psf5.dat};
			\addlegendentry{PSF (25)}
			\addplot[purple, line width=0.5mm] table {advDiff_cg_rand_errs_psf25.dat};
		\end{axis}
	\end{tikzpicture}
\end{document}

>>>>

\begin{document}
			\begin{tikzpicture}[baseline]%, trim axis right]
			\begin{axis}[width=0.49\linewidth, height=0.5\linewidth,
	ymode=log,
	ymin=1e-13,
	ymax=2,
	xmax=750,
	axis x line*=bottom,
	axis y line*=left,
	xtick={0, 200, 400, 600},
	title={CG convergence},
	xlabel={$k$, CG iteration},
	ylabel={$\|\bm{x}_k-\bm{x}\|/\|\bm{x}\|$},
	legend style={at={(1.2,1)},anchor=north east,draw=none},
	%legend pos=north east,
	legend style={font=\small}
	]
	\addlegendentry{Reg}		
	\addplot[dotted, line width=0.5mm] table {cg_relres_reg_0.05noise.dat};
	\addlegendentry{None}
	\addplot[dash dot, line width=0.5mm] table {cg_relres_none_0.05noise.dat};
	\addlegendentry{PSF (1)}
	\addplot[blue, line width=0.5mm] table {cg_relres_psf1_0.05noise.dat};
	\addlegendentry{PSF (5)}
	\addplot[red, line width=0.5mm] table {cg_relres_psf5_0.05noise.dat};
	\addlegendentry{PSF (25)}
	\addplot[purple, line width=0.5mm] table {cg_relres_psf25_0.05noise.dat};
	\end{axis}
	\end{tikzpicture}
\end{document}
